---
title: "Report on CS Freshmen in 20210 to 202120"
author: "Akhil Kadarla"
date: "3/2/2022"
output: rmarkdown::github_document
---

I have the data of all the students starting from 
the spring of 2017(201620) to the spring of 2022(202120). This report has the data of the freshmen in fall of 2021, spring of 2022. 

**Data of freshmen in Fall of 2021(202110):**

```{r}
library("readxl")
Data202110FR<-read_excel('Data202110FR.xlsx')
Data202110FR
```
There are 170 Freshmen who joined as CS majors in the Fall of 2021(202110). 

**Data of freshmen in Spring of 2021(202120):**

```{r}
library("readxl")
Data202120FR<-read_excel('Data202120FR.xlsx')
Data202120FR
```
There are 149 Freshmen who joined as CS majors in the spring of 2021(202120). 


**Data of students who continued as freshmen from 202110 to 202120:**
```{r}
library("readxl")
Freshmen2021_22<-read_excel('Freshmen2021-22.xlsx')
Freshmen2021_22
```
**Data of students who joined as freshmen 202120:**

```{r}
library("readxl")
Freshmen_202120<-read_excel('New_joinings.xlsx')
Freshmen_202120
```

Above is the list of students who continued as freshmen to the next semester. 

From the data , we can see that there were 170 students as freshmen in the fall of 2021 and 149 students students as freshmen in the spring of 2021. 30 joined as freshman in Spring of 2021. 119 continued to as freshmen from fall 2021 to spring 2021. There is a difference of 51 students when compared.
This could be either the students have changed their major  or moved to a higher class  or left the university. 
